The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-14 paper.tex
update 'Ontological Architecture'

  \item GFO is a top-level ontology and is used for integrating and founding the ANNO. In the current paper, we refer especially to the categories 
\aurl{gfo}{Material_object}, \aurl{gfo}{Attributive}, \aurl{gfo}{Relator} as well as the spatial entities of GFO, \aurl{gfo}{Line_region} and \aurl{gfo}{Surface_region} (\cref{sec:core}, \cref{fig:gfo}).
\end{enumerate}

>>>>

  \item GFO is a top-level ontology and is used for integrating and founding the ANNO. In the current paper, we refer especially to the categories 
\enquote{Material object}, \enquote{Attributive}, \enquote{Relator} as well as the spatial entities of GFO (\cref{sec:core}, \cref{fig:gfo}).
\end{enumerate}
